---
title: "Robust_estimator"
author: "zhao hongqiang"
date: "5/24/2021"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#install.packages("fpp2")
#install.packages("robustbase")
library(fpp2)
data(uschange)
library(robustbase)
library(MASS)
```
# Robust estimator of a parameter of the probability distribution
data choise Percentage changes in quarterly personal consumption expenditure, personal disposable income, production, savings and the unemployment rate for the US, 1960 to 2016.

```{r}
summary(uschange)
head(uschange)
```

```{r}
plot(uschange)
```

## Robust parameter estimation, using M estimation

M-estimation defines a weight function such that the estimating equation becomes $\sum_{i=1}^{n} w_{i}\left(y_{i}-x^{\prime} b\right) x_{i}^{\prime}=0$
. But the weights depend on the residuals and the residuals on the weights

```{r}

MM=rlm(Consumption ~ Income + Production + Unemployment + Savings,
    data=uschange)
summary(MM)
```
```{r}
hweights <- data.frame( resid = MM$resid, weight = MM$w)
hweights2 <- hweights[order(MM$w), ]
hweights2[1:15, ]
```
We can see that roughly, as the absolute residual goes down, the weight goes up.




